### 2025-07-05 machine-learning.qmd
20250705 - machine learning summary?

```{r}
library("petersenlab")
library("parallel")
library("future")
library("missRanger")
library("powerjoin")
library("tidymodels")
library("LongituRF")
library("gpboost")
library("effectsize")
library("tidyverse")
```

@@

# Define Recipe (Formula)
rec <- recipes::recipe(
  fantasyPoints_lag ~ ageCentered20,
  data = data_train_qb)

@@

@@

@@

@@

@@

@@

#### Cross-Sectional Data {#sec-randomForestCrossSectionalData}

@@

@@

#### Longitudinal Data {#sec-randomForestLongitudinalData}

@@

smerf$forest # the fitted random forest (obtained at the last iteration)
smerf$random_effects %>% data.frame() # the predicted random effects for each player
smerf$omega %>% data.frame() # the predicted stochastic processes
smerf$OOB # OOB error at each iteration

# Predict on Test Data
predict(
  smerf,
  X = data_test_qb %>% dplyr::select(season:att_br.rush) %>% as.matrix(),
  Z = data_train_qb %>% dplyr::mutate(constant = 1) %>% dplyr::select(constant, passing_yards, passing_tds, passing_interceptions, passing_epa, pacr) %>% as.matrix(),
  id = data_test_qb[,c("gsis_id")] %>% as.matrix(),
  time = data_test_qb[,c("ageCentered20")] %>% as.matrix())
```

@@

@@

@@

>>>>

```{r}
library("petersenlab")
library("parallel")
library("future")
library("missRanger")
library("powerjoin")
library("tidymodels")
library("LongituRF")
library("gpboost")
library("effectsize")
library("tidyverse")
library("knitr")
```

@@

# Define Recipe (Formula)
rec <- recipes::recipe(
  fantasyPoints_lag ~ fantasyPoints,
  data = data_train_qb)

@@

rsquare_onePredictor <- petersenlab::accuracyOverall(
  predicted = df$pred,
  actual = df$fantasyPoints_lag,
  dropUndefined = TRUE
)$rsquared %>% round(., digits = 2)
```

@@

rsquare_multiplePredictors <- petersenlab::accuracyOverall(
  predicted = df$pred,
  actual = df$fantasyPoints_lag,
  dropUndefined = TRUE
)$rsquared %>% round(., digits = 2)
```

@@

rsquare_lasso <- petersenlab::accuracyOverall(
  predicted = df$pred,
  actual = df$fantasyPoints_lag,
  dropUndefined = TRUE
)$rsquared %>% round(., digits = 2)
```

@@

rsquare_ridge <- petersenlab::accuracyOverall(
  predicted = df$pred,
  actual = df$fantasyPoints_lag,
  dropUndefined = TRUE
)$rsquared %>% round(., digits = 2)
```

@@

rsquare_elasticNet <- petersenlab::accuracyOverall(
  predicted = df$pred,
  actual = df$fantasyPoints_lag,
  dropUndefined = TRUE
)$rsquared %>% round(., digits = 2)
```

@@

#### Assuming Independent Observations {#sec-randomForestIndependent}

@@

rsquare_randomForest <- petersenlab::accuracyOverall(
  predicted = df$pred,
  actual = df$fantasyPoints_lag,
  dropUndefined = TRUE
)$rsquared %>% round(., digits = 2)
```

@@

#### Accounting for Longitudinal Data {#sec-randomForestLongitudinalData}

@@

smerf$forest # the fitted random forest (obtained at the last iteration)
smerf$random_effects %>% data.frame() # the predicted random effects for each player
smerf$omega %>% data.frame() # the predicted stochastic processes
smerf$OOB # OOB error at each iteration
```

@@

The following code generates an error, for some reason.
This issue has been posted on the GitHub repository: <https://github.com/sistm/LongituRF/issues/5>.
Hopefully the package maintainer will help address the issue.

```{r}
# Predict on Test Data
predict(
  smerf,
  X = data_test_qb %>% dplyr::select(season:att_br.rush) %>% as.matrix(),
  Z = data_train_qb %>% dplyr::mutate(constant = 1) %>% dplyr::select(constant, passing_yards, passing_tds, passing_interceptions, passing_epa, pacr) %>% as.matrix(),
  id = data_test_qb[,c("gsis_id")] %>% as.matrix(),
  time = data_test_qb[,c("ageCentered20")] %>% as.matrix())
```

@@

rsquare_treeBoosting <- petersenlab::accuracyOverall(
  predicted = predictedVsActual$predictedPoints,
  actual = predictedVsActual$actualPoints,
  dropUndefined = TRUE
)$rsquared %>% round(., digits = 2)
```

@@

## Summarizing the Machine Learning Models {#sec-summarizingModels-machineLearning}

machineLearningTable <- data.frame(
  model = c(
    "Regression with One Predictor",
    "Regressions with Multiple Predictors",
    "LASSO",
    "Ridge Regression",
    "Elastic Net",
    "Random Forest",
    "Tree-Boosting"
  ), 
  rsquared = c(
    rsquare_onePredictor,
    rsquare_multiplePredictors,
    rsquare_lasso,
    rsquare_ridge,
    rsquare_elasticNet,
    rsquare_randomForest,
    rsquare_treeBoosting
  )
)
```

```{r}
#| label: tbl-machineLearningModelSummary
#| tbl-cap: "Summary of Machine Learning Models."
#| echo: false

knitr::kable(
  machineLearningTable,
  col.names = c("Model","$R^2$"),
  booktabs = TRUE)
```

### 2025-07-05 multiple-regression.qmd
20250705 - machine learning summary?

kable(
  regression1,
  col.names = c("y","x1"),
  booktabs = TRUE)
```

@@

kable(
  regression2,
  col.names = c("y","x1","x2"),
  booktabs = TRUE)
```

@@

kable(
  regression3,
  col.names = c("y","x1","x2"),
  booktabs = TRUE)
```

>>>>

knitr::kable(
  regression1,
  col.names = c("y","x1"),
  booktabs = TRUE)
```

@@

knitr::kable(
  regression2,
  col.names = c("y","x1","x2"),
  booktabs = TRUE)
```

@@

knitr::kable(
  regression3,
  col.names = c("y","x1","x2"),
  booktabs = TRUE)
```
